Polynomial phase estimation by phase unwrapping

### 2012-10-17 paper.tex
minor

\begin{lemma}\label{lem:Kconvfhalf}
With $K_{\ell,N}$ defined in~\eqref{eq:KellN}, $h = f(-\nicefrac{1}{2})$, and $C_{\ell k} =  \frac{1}{\ell + k + 1}$ we have $K_{\ell,N} = (h - 1) \sqrt{N} \sum_{k=0}^{m}  \widehat{\psi}_{k,N} \big( C_{\ell k} + o_P(1) \big) + o_P(1)$ for all $\ell = 0, \dots, m$.% is an element of the $m+1$ by $m+1$ Hilbert matrix, and $o_P(1)$ denotes a random variable converging in probability to zero as $N\rightarrow\infty$.
\end{lemma}
\begin{proof}
Care must be taken since $\widehat{\psibf}_N$ depends on the sequence $\{ \Phi_n \}$.  For $n = 1, \dots, N$ and positive $N$, let
\begin{equation}
p_{nN}(\psibf) = \sum_{k=0}^{m}\left( \tfrac{n}{N}\right)^k \psi_k,
\end{equation}
and put $q_{n}(x) = \round{\Phi_n + x}$ and $Q(x) = \expect q_{n}(x) =  \expect q_{1}(x)$.  Let
\begin{equation}\label{eq:GNdef}
G_{\ell,N}(\psibf) = \frac{1}{\sqrt{N}} \sum_{n=1}^{N}\left( \tfrac{n}{N}\right)^\ell  \big(q_n(p_{nN}(\psibf)) - Q(p_{nN}(\psibf)) \big),
\end{equation}
and put
\begin{equation}\label{eq:hatpnN}
\widehat{p}_{nN} = p_{nN}(\widehat{\psibf}_N) = \sum_{k=0}^m \left(\tfrac{n}{N}\right)^k \widehat{\psi}_{k,N}.
\end{equation}
Now $W_n$ from~\eqref{eq:Wn} can be written as $W_n = \round{\Phi_n + \widehat{p}_{nN}} = q_{n}(\widehat{p}_{nN})$ and $K_{\ell,N}$ from~\eqref{eq:KellN} can be written as
\begin{align*}
K_{\ell,N} &= \frac{1}{\sqrt{N}}\sum_{n=1}^{N}(\tfrac{n}{N})^\ell\big( q_{n}(\widehat{p}_{nN}) - \widehat{p}_{nN}  \big) \\
&= \frac{1}{\sqrt{N}}\sum_{n=1}^{N}(\tfrac{n}{N})^\ell\big(q_{n}(\widehat{p}_{nN}) - \widehat{p}_{nN} + Q(\widehat{p}_{nN}) - Q(\widehat{p}_{nN}) \big) \\
&= G_{\ell,N}(\widehat{\psibf}_N) + H_{\ell,N},
\end{align*}
where 
\begin{equation}\label{eq:HellNdef}
H_{\ell,N} = \frac{1}{\sqrt{N}}\sum_{n=1}^{N}(\tfrac{n}{N})^\ell \big( Q(\widehat{p}_{nN}) - \widehat{p}_{nN} \big).
\end{equation}
Lemma~\ref{lem:unifprobG} in the Appendix shows that for any $\delta >0$ and $\nu > 0$ there exists an $\epsilon > 0$ such that
\[
\prob\left\{ \sup_{\|\psibf\|_{\infty} < \epsilon} \abs{ G_{\ell,N}(\psibf) } > \delta   \right\} < \nu
\]
for all positive integers $N$ and all $\ell = 0,\dots,m$, where $\|\psibf\|_\infty = \sup_{k} \abs{\psi_k}$.  Since $\widehat{\psibf}_N$ converges almost surely to zero, it follows that $\lim_{N\rightarrow\infty}\prob\left\{ \|\widehat{\psibf}_N\|_{\infty} \geq \epsilon \right\} = 0$ for any $\epsilon > 0$, and therefore $\prob\{ \|\widehat{\psibf}_N\|_{\infty} \geq \epsilon \} < \nu$ for all sufficiently large $N$.  Now
\begin{align*}
  \prob\left\{\abs{ G_{\ell,N}(\widehat{\psibf}_N) } > \delta \right\} &= \prob\left\{ \abs{G_{\ell,N}(\widehat{\psibf}_N)} > \delta \;, \; \|\widehat{\psibf}_N\|_{\infty} < \epsilon \right\} \\
&\hspace{1cm} + \prob\left\{ \abs{G_{\ell,N}(\widehat{\psibf}_N)} > \delta  \;, \; \|\widehat{\psibf}_N\|_{\infty} \geq \epsilon \right\} \\
&\leq \prob\left\{  \sup_{\|\psibf\|_{\infty} < \epsilon} \abs{ G_{\ell,N}(\psibf) } > \delta \right\} + \prob\left\{ \|\widehat{\psibf}_N\|_{\infty} \geq \epsilon \right\} \\
&\leq 2\nu
\end{align*}
for all sufficiently large $N$.  Since $\nu$ and $\delta$ can be chosen arbitrarily small, it follows that $G_{\ell,N}(\widehat{\psibf}_N)$ converges in probability to zero as $N\rightarrow\infty$, and therefore $K_{\ell,N} = H_{\ell,N} + o_P(1)$.  Lemma~\ref{lem:sumpNhilb} shows that
\begin{align*}
H_{\ell,N} =  (h-1)\sqrt{N} \sum_{k=0}^{m}  \widehat{\psi}_{k,N} \big(C_{\ell k} + o_P(1)\big).
\end{align*}
%The proof follows.
\end{proof}

>>>>

\begin{lemma}\label{lem:Kconvfhalf}
With $K_{\ell,N}$ defined in~\eqref{eq:KellN}, $h = f(-\nicefrac{1}{2})$, and $C_{\ell k} =  \frac{1}{\ell + k + 1}$ we have $K_{\ell,N} = (h - 1) \sqrt{N} \sum_{k=0}^{m}  \widehat{\psi}_{k,N} \big( C_{\ell k} + o_P(1) \big) + o_P(1)$ for all $\ell = 0, \dots, m$.% is an element of the $m+1$ by $m+1$ Hilbert matrix, and $o_P(1)$ denotes a random variable converging in probability to zero as $N\rightarrow\infty$.
\end{lemma}
\begin{proof}
Care must be taken since $\widehat{\psibf}_N$ depends on the sequence $\{ \Phi_n \}$.  For $n = 1, \dots, N$ and positive $N$, let
\begin{equation}
p_{nN}(\psibf) = \sum_{k=0}^{m}\left( \tfrac{n}{N}\right)^k \psi_k,
\end{equation}
and put $q_{n}(x) = \round{\Phi_n + x}$ and $Q(x) = \expect q_{n}(x) =  \expect q_{1}(x)$.  Let
\begin{equation}\label{eq:GNdef}
G_{\ell,N}(\psibf) = \frac{1}{\sqrt{N}} \sum_{n=1}^{N}\left( \tfrac{n}{N}\right)^\ell  \big(q_n(p_{nN}(\psibf)) - Q(p_{nN}(\psibf)) \big),
\end{equation}
and put
\begin{equation}\label{eq:hatpnN}
\widehat{p}_{nN} = p_{nN}(\widehat{\psibf}_N) = \sum_{k=0}^m \left(\tfrac{n}{N}\right)^k \widehat{\psi}_{k,N}.
\end{equation}
Now $W_n$ from~\eqref{eq:Wn} can be written as $W_n = \round{\Phi_n + \widehat{p}_{nN}} = q_{n}(\widehat{p}_{nN})$ and $K_{\ell,N}$ from~\eqref{eq:KellN} can be written as
\begin{align*}
K_{\ell,N} &= \frac{1}{\sqrt{N}}\sum_{n=1}^{N}(\tfrac{n}{N})^\ell\big( q_{n}(\widehat{p}_{nN}) - \widehat{p}_{nN}  \big) \\
&= \frac{1}{\sqrt{N}}\sum_{n=1}^{N}(\tfrac{n}{N})^\ell\big(q_{n}(\widehat{p}_{nN}) - \widehat{p}_{nN} + Q(\widehat{p}_{nN}) - Q(\widehat{p}_{nN}) \big) \\
&= G_{\ell,N}(\widehat{\psibf}_N) + H_{\ell,N},
\end{align*}
where 
\begin{equation}\label{eq:HellNdef}
H_{\ell,N} = \frac{1}{\sqrt{N}}\sum_{n=1}^{N}(\tfrac{n}{N})^\ell \big( Q(\widehat{p}_{nN}) - \widehat{p}_{nN} \big).
\end{equation}
Lemma~\ref{lem:unifprobG} in the Appendix shows that for any $\delta >0$ and $\nu > 0$ there exists an $\epsilon > 0$ such that
\[
\prob\left\{ \sup_{\|\psibf\|_{\infty} < \epsilon} \abs{ G_{\ell,N}(\psibf) } > \delta   \right\} < \nu
\]
for all positive integers $N$ and all $\ell = 0,\dots,m$, where $\|\psibf\|_\infty = \sup_{k} \abs{\psi_k}$.  Since $\widehat{\psibf}_N$ converges almost surely to zero, it follows that 
\[
\lim_{N\rightarrow\infty}\prob\left\{ \|\widehat{\psibf}_N\|_{\infty} \geq \epsilon \right\} = 0
\]
for any $\epsilon > 0$, and therefore $\prob\{ \|\widehat{\psibf}_N\|_{\infty} \geq \epsilon \} < \nu$ for all sufficiently large $N$.  Now
\begin{align*}
  \prob\left\{\abs{ G_{\ell,N}(\widehat{\psibf}_N) } > \delta \right\} &= \prob\left\{ \abs{G_{\ell,N}(\widehat{\psibf}_N)} > \delta \;, \; \|\widehat{\psibf}_N\|_{\infty} < \epsilon \right\} \\
&\hspace{1cm} + \prob\left\{ \abs{G_{\ell,N}(\widehat{\psibf}_N)} > \delta  \;, \; \|\widehat{\psibf}_N\|_{\infty} \geq \epsilon \right\} \\
&\leq \prob\left\{  \sup_{\|\psibf\|_{\infty} < \epsilon} \abs{ G_{\ell,N}(\psibf) } > \delta \right\} + \prob\left\{ \|\widehat{\psibf}_N\|_{\infty} \geq \epsilon \right\} \\
&\leq 2\nu
\end{align*}
for all sufficiently large $N$.  Since $\nu$ and $\delta$ can be chosen arbitrarily small, it follows that $G_{\ell,N}(\widehat{\psibf}_N)$ converges in probability to zero as $N\rightarrow\infty$, and therefore $K_{\ell,N} = H_{\ell,N} + o_P(1)$.  Lemma~\ref{lem:sumpNhilb} shows that
\begin{align*}
H_{\ell,N} =  (h-1)\sqrt{N} \sum_{k=0}^{m}  \widehat{\psi}_{k,N} \big(C_{\ell k} + o_P(1)\big).
\end{align*}
%The proof follows.
\end{proof}
